Elephant Seal Age JAE Intraspecific Variation

### 2023-12-07 paper/paperv3.qmd
Adding supplemental figures and tables

We found that as maternal age increases, pup sex skews slightly towards males - but it's not significant.

@@

tbl_breed_cap <- str_glue("The results from breeding probability analyis. The random effect variance of animal id is {format_signif(VarCorr(breeding_mod)$animalID, 3)} and of year was {format_signif(VarCorr(breeding_mod)$year, 3)}.")

@@

Supplemental table for sex ratios

@@

>>>>

We found that as maternal age increases, pup sex skews slightly towards males.

@@

tbl_breed_cap <- str_glue("The results from breeding probability analysis. The random effect variance of animal id is {format_signif(VarCorr(breeding_mod)$animalID, 3)} and of year was {format_signif(VarCorr(breeding_mod)$year, 3)}.")

@@

Supplemental table for offspring survival

```{r}
surv_mod_summary <- summary(pup_surv_model)
surv_mod_kable <- surv_mod_summary$coefficients %>% 
  as_tibble() %>% 
  mutate(Parameter = c("Intercept", "Age (linear)", "Age (quadratic)"),
         across(c(Estimate, `Std. Error`, `z value`), 
                \(x) format_signif(x, digits = 3)),
         `p value` = format_pval(`Pr(>|z|)`, digits = 2),
         Response = "Survival") %>%
  select(-`Pr(>|z|)`) %>% 
  relocate(Response, Parameter)

recruit_mod_summary <- summary(pup_recruit_model)
recruit_mod_kable <- recruit_mod_summary$coefficients %>% 
  as_tibble() %>% 
  mutate(Parameter = c("Intercept", "Age (linear)", "Age (quadratic)"),
         across(c(Estimate, `Std. Error`, `z value`), 
                \(x) format_signif(x, digits = 3)),
         `p value` = format_pval(`Pr(>|z|)`, digits = 2),
         Response = "Recruitment") %>%
  select(-`Pr(>|z|)`) %>% 
  relocate(Response, Parameter)

rbind(surv_mod_kable, recruit_mod_kable) %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::collapse_rows(columns = 1)
```

Supplemental table for pup sex ratio model.

```{r}
pupsex_mod_summary <- summary(pup_sex_mod)
pupsex_mod_summary$coefficients %>% 
  as_tibble() %>% 
  mutate(Parameter = c("Intercept", "Age (linear)"),
         across(c(Estimate, `Std. Error`, `z value`), 
                \(x) format_signif(x, digits = 3)),
         `p value` = format_pval(`Pr(>|z|)`/2, digits = 3)) %>%
  select(-`Pr(>|z|)`) %>% 
  relocate(Parameter) %>% 
  knitr::kable()

# We fit a quadratic equation, but only the linear term was significant, so the linear model is the one that is plotted. take the p = 0.517 and divide by 2 because a priori. report in supplemental table that its reporting on 1 tailed (no absolute value of z, just z)
```

Supplemental table for male biased sex ratios at older ages.

@@

Supplemental figure for phenology models

#NOTE: Both BA and BD have some points that are really late (above 300 doy) that need fixing
BA_age <- ggplot(seal_phenology, aes(age, BA)) + 
  geom_point() + 
  scale_y_continuous(limits = c(0, 150)) + 
  theme_classic() + 
  labs(y = "Breeding arrival (DOY)", x = "Maternal age (Years)")

BD_age <- ggplot(seal_phenology, aes(age, BD)) + 
  geom_point() + 
  scale_y_continuous(limits = c(0, 150)) + 
  theme_classic() + 
  labs(y = "Breeding departure (DOY)", x = "Maternal age (Years)")

MA_age <- ggplot(seal_phenology, aes(age, MA)) + 
  geom_point() + 
  geom_smooth(method = "lm", color = "#829BD1") + 
  scale_y_continuous(limits = c(50, 200)) + 
  theme_classic() + 
  labs(y = "Molt arrival (DOY)", x = "Maternal age (Years)")

MD_age <- ggplot(seal_phenology, aes(age, MD)) + 
  geom_point() + 
  geom_smooth(method = "lm", color = "#829BD1") + 
  scale_y_continuous(limits = c(50, 200)) + 
  theme_classic() + 
  labs(y = "Molt departure (DOY)", x = "Maternal age (Years)")

plot_grid(BA_age, BD_age, MA_age, MD_age, nrow = 2, ncol = 2)
```

Supplemental table for the phenology models.

```{r}
BA_summary <- phenology_models$model[1]
 <- BA_summary$coefficients %>% 
  as_tibble() %>% 
  mutate(Parameter = c("Intercept", "Age (linear)", "Age (quadratic)"),
         across(c(Estimate, `Std. Error`, `z value`), 
                \(x) format_signif(x, digits = 3)),
         `p value` = format_pval(`Pr(>|z|)`, digits = 2),
         Response = "Survival") %>%
  select(-`Pr(>|z|)`) %>% 
  relocate(Response, Parameter)

recruit_mod_summary <- summary(pup_recruit_model)
recruit_mod_kable <- recruit_mod_summary$coefficients %>% 
  as_tibble() %>% 
  mutate(Parameter = c("Intercept", "Age (linear)", "Age (quadratic)"),
         across(c(Estimate, `Std. Error`, `z value`), 
                \(x) format_signif(x, digits = 3)),
         `p value` = format_pval(`Pr(>|z|)`, digits = 2),
         Response = "Recruitment") %>%
  select(-`Pr(>|z|)`) %>% 
  relocate(Response, Parameter)

rbind(surv_mod_kable, recruit_mod_kable) %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::collapse_rows(columns = 1)
```
